---
title: "Parse Antismash"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Parse Antismash}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This notebook parses antismash and it is heavily inspired in the work of XXX. 

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Set up

```{r setup}
library(RauENVS)
antismash_directory <- system.file(
  "antismash_example_directory",package =  "RauENVS"
  )
# Edit this to your actual file!!! and remove or comment the example file
# For example:
# antismash_directory <- "User/MyPath/antismash"
```

First, we need to identify the json files:

```{r json}
list_jsons <- function(dir) list.files(
  dir, ".json$", full.names = T,recursive = T,include.dirs = T
  )
(jsons <- list_jsons(antismash_directory))
(genome_ids <- stringr::str_match(basename(jsons), "(^.+)\\.json")[,2])
names(jsons) <- genome_ids
```

## Get features

Now, we want to extract the features for each json file. 

```{r features}
features <- get_antismash_features(jsons)
```


Features is a large list, so inspect it carefully. It should have as many lists as json files:

```{r sanity_check}
stopifnot(length(features) == length(jsons))
```

## Regions

Now, we are extracting all regions:

```{r regions}
(regions <- get_antismash_regions(features))
# write.csv(regions, "region.csv")
```

You will notice that the product column is nested (each cell is a list of values). You can either *paste* the different values:

```{r paste}
regions |>
  dplyr::mutate(
    product = purrr::map(product, paste0, collapse = ",") |>
      as.character()
    )
```

Or you can unnest the DataFrame by creating a new row per each product:

```{r unnest}
regions |>
  tidyr::unnest("product")
```

## Modules

Now, we extract the modules:

```{r modules}
(modules <- get_antismash_modules(features))
# write.csv(modules, "modules.csv")

```

